Data Responsive-report

### 2021-02-04 GALI_2020.Rmd
index issues

#Initial FE regression without controls 
```{r}
gali_fe_mod <- plm(revenue ~ (attention_fc*inst_fc_gci) , 
                   data = revenue_data, 
                   index = c("country", "year"),
                   model = "within")

>>>>

#Initial FE regression without controls 
```{r}
revenue_data <- transform(revenue_data, id=match(paste(revenue_data$country,revenue_data$New_External_ID,sep="_"), unique(paste(revenue_data$country,revenue_data$New_External_ID,sep="_")))) #create a column called id which assigns a unique id to the unique combinations of origin and destination countries

gali_fe_mod <- plm(revenue ~ (attention_fc*inst_fc_gci) , 
                   data = revenue_data, 
                   index = c("id", "year"),
                   model = "within")
